---
title: '<font size = 7 color = "skyblue">W05.1: Sampling Distribution of Sample Means </font>'
subtitle: '<font size = 6 color = "gold"> - Applications of Central Limit Theorem</font>'
author: '<font size = 6 color = "skyblue">Cheng Peng </font>'
institute: '<font size = 5 color = "skyblue">West Chester University of Pennsylvania</font><br>'
date: '<font color = "skyblue" size =5> 09/29/2022 <font> <br> <font color = "skyblue" size =4>  </font> <br> <font color = "gold" size = 6> MAT 121 - Statistics I </font> <br> <br> <font color = "white" size = 5> Slides available at: https://pengdsci.github.io/MAT121/w05-CLTHTMLPresentation.html</font>'
output:
  xaringan::moon_reader:
    #yolo: true  #randomly insert new slides with background image of Karl’s mustache photo into existing slides
    lib_dir: libs
    self_contained: true
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: true
      #titleSlideClass: [center, middle, inverse]  # default set up of the title page
      #titleSlideClass: [top, left, inverse]
      #autoplay: 30000     # This sets autoplay, 30000 = 10 seconds
      #countdown: 30000    # The timer will count down to 00:00 then continue with red time
---



```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
##
if(!require('xaringan')) {
  remotes::install_github("yihui/xaringan")
  library('xaringan')
}
if (!require("knitr")) {
   install.packages("knitr")
   library(knitr)
}
if (!require("leaflet")) {
   install.packages("leaflet")
   library(leaflet)
}
# remotes::install_github("yihui/xaringan")
```



class: inverse, middle   
<!-- This sets the background color to black and align the text in the slide -->
<!-- Comments must be placed after the line of the page of configuration and also 
     be placed in separate lines.  --> 
<!-- use "---" to close each slide -->
<!-- not comments should placed immediately before "---" -->

## <center><b>Agenda </b></center>    
<!-- level 2 title -->

### Distribution of Sample Means - A Simulation

### Centrl Limit Theorem (CLT)

### Applications of CLT

### Use of IntroStatsApps

---




class: inverse, center, middle
<!-- inverse option -->

# <font color = "gold">Sampling Distribution of Sample Means </font>

<br>

### <font color = "gold"> In order to investiage the pasture rent structure with respect to the grass variety

</font>
---










class: middle
<!-- some comments -->

## <center>Data Source and Variable Description</center>

### Source

The data (https://people.sc.fsu.edu/~jburkardt/datasets/regression/x11.txt) were collected over various districts in Minnesota.

### Description

There are 67 rows  and 4 variables in the data set (the first column is the observation ID).
      
**ArablePrice**: the rent per acre of arable land,
      
**CowsCount**: the number of milk cows per square mile,
      
**DiffPastureArable**: the difference between pasturage and arable land,
      
**PastreRentalPrice**:  the rental price per acre for this variety of grass.  
---



## <center> Exploratory Data Analysis (EDA) </center> 

```{r echo = FALSE, fig.align='center'}
rental.data = read.table("https://people.sc.fsu.edu/~jburkardt/datasets/regression/x11.txt", skip = 38)[,-1]
names(rental.data) = c("ArablePrice", "CowsCount", "DiffPastureArable", "PastreRentalPrice") 
pairs(rental.data, main="Pair-wise Scatter Plots of Pasture Rental Data")
```

---

class: center, middle
<!-- inverse option -->

## <center>Linear Regression: Initial Model and Diagnostics</center>

```{r echo = FALSE}
m0 = lm(PastreRentalPrice ~ ArablePrice + CowsCount + DiffPastureArable, data = rental.data)
coef.mtx = summary(m0)$coef
kable(coef.mtx)
```

```{r echo = FALSE, fig.align='center', fig.width=8, fig.height=4}
par(mfrow= c(1,2) )
plot(m0)
```
---




class: middle

## <center> Results and Discussions </center>
<!-- commenting  -->

- The residual plots indicates that some potential violations of model assumptions

  1. The variance is not a contant
  
  2. There are three potential outliers.
  
- Refit the model by dropping the insignificant variable

```{r echo = FALSE}
m1 = lm(PastreRentalPrice ~ ArablePrice + CowsCount, data = rental.data)
coef.mtx1 = summary(m1)$coef
kable(coef.mtx1)
```


---


```{r echo = FALSE, fig.align='center', fig.width=8, fig.height=8}
par(mfrow= c(2,2) )
plot(m1)
```


---



class: middle

## <center> Final Model and Conclusions </center>
<!-- commenting  -->


---




class: inverse, center, middle

# Thanks!




